Title goes here

### 2016-10-23 paper/paper.tex
Added citations

Most of aircraft are provided with ADB-S transmitter, which send continuosly
information about the status and the position of the aircraft to guarantee
better air traffic control. The messages are not encripted and, in most region,
this technology will become mandatory in 2020. For these reasons OpenSky network
was recently born.

@@

A way to reduce the number of air routes is illustrated in \textit{J. DeArmon et
  al, Air Route Clustering for a Queuing Network Model of the National Airspace
  System}. The research showed that similar routes can be grouped to reduce the
number of path between a pair of airports thus decrease air traffic congestion.
The same approach could be used to detect standard routes where aircraft fly,
given the departure and arrival airports. The first prototype of this model has
been developed to improve the air traffic flow in the National Airspace System
of the USA.

>>>>

Most of aircraft are provided with ADB-S transmitter, which send continuosly
information about the status and the position of the aircraft to guarantee
better air traffic control. The messages are not encripted and, in most region,
this technology will become mandatory in 2020. For these reasons OpenSky network
was recently born\cite{opensky}.

@@

A way to reduce the number of air routes is illustrated bt J. DeArmon.
The research showed that similar routes can be grouped to reduce the
number of path between a pair of airports thus decrease air traffic 
congestion\cite{routeclustering}. The same approach could be used to detect
standard routes where aircraft fly, given the departure and arrival airports.
The first prototype of this model has been developed to improve the air traffic
flow in the National Airspace System of the USA.
